---
title: "Example"
author: "Jan Caha"
date: "11 12 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load necessary packages.

```{r, warning=FALSE, message=FALSE}
library(raster)
library(geoviz)
library(rasterShade)
library(tmap)
library(scales)
library(cartography)
```

Get digital elevation model for part ot Tatra Mountains (Slovakia).

```{r,  warning=FALSE, message=FALSE}
dem <- mapzen_dem(lat = 49.16770, long = 20.13074, square_km = 10, width_buffer = 1, max_tiles = 10)
```

Store the original coordinate reference system (CRS) and project the raster into projected coordinate system, so that the calculation makes sense.

```{r, warning=FALSE, message=FALSE}
crs_original <- crs(dem)

crs_projected <- CRS("+init=epsg:5514")

dem <- projectRaster(dem, crs = crs_projected)
```

Calculate global and lambert shade raster.

```{r}
shade_raster <- shade_global_sun_position(dem, sun_elevation = 25, sun_azimuth = 135)
shade_lambert_raster <- shade_lambert_sun_position(dem, sun_elevation = 25, sun_azimuth = 135)
```

Project rasters back to their original CRS for visualization.

```{r, warning=FALSE, message=FALSE}
dem <- projectRaster(dem, crs = crs_original)
shade_raster <- projectRaster(shade_raster, crs = crs_original)
shade_lambert_raster <- projectRaster(shade_lambert_raster, crs = crs_original)
```

Create color palettes for dem and shadows (including opacity),

```{r}
surface_pal <- terrain.colors(10)

shadow_pal <- carto.pal("grey.pal", 10)
```

Merge shadows together.
```{r}
shade_together <- shade_raster + shade_lambert_raster 
```

Create resulting visualization.

```{r}
tm_shape(dem) +
  tm_raster(palette = surface_pal, style = "cont") +
tm_shape(shade_together) +
  tm_raster(palette = rev(shadow_pal), style = "cont", alpha = 0.5) +
tm_layout(legend.show = FALSE,
          frame = "white")
```
